Unrecognized States: Theory and Cases

### 2017-07-03 theory.tex
take out payoff notation for outside actors, state variable notation

All the state variables except for the secessionists' status quo payoffs remain unchanged from period to period unless players $p$ or $c$ make an investment. To be precise, we have\footnote{Here we anticipate a bit the incentives of the patron and international community to sign the impact of contributions in each case.}
	\begin{equation}
	\begin{aligned}
		L_s^t = L_s^{t-1} - R_p^t + R_c^t \hskip.5in L_g^t = L_g^{t-1} + R_p^t - R_c^t \\
		W_s^t = W_s^{t-1} + R_p^t - R_c^t \hskip.5in W_g^t = W_g^{t-1} - R_p^t + R_c^t \\
		Q_g^t = Q_g^{t-1} - R_p^t + R_c^t \hskip.5in Q_s^t = Q_s^{t-1} - \mu + R_p^t - R_c^t
		\label{eqn:motion}
	\end{aligned}
	\end{equation}

The status quo payoffs for the secessionists are special in that the transition of this state variable from one period to the next involves an automatic reduction by $\mu$. The steady reduction by $\mu$ represents the costs of non-recognition discussed in the introduction.

Only two outcomes of the stage game do not lead to absorbing states, and the payoffs for these are bolded. If both $s$ and $g$ play Status Quo, then the status quo persists. Likewise, if both states simultaneously play Cede, we assume that both renege immediately and that the status quo is preserved for that period. In this case neither player has demonstrated a willingness to give up more than the other. Therefore, payoffs for both players ceding simultaneously are identical to the status quo payoffs.%\footnote{This assumption is appropriate as precise simultaneity is an artifact of discrete time modeling: it is not a phenomenon we observe in the real world.}

@@

We use two binary variables to express the preferences among the three outcomes (status quo, reunification, recognition by the home state) for both $p$ and $c$. $X$ represents reunification: $X=0$ in the status quo and $X=1$ if the secessionists rejoin the home state. Y represents recognition: $Y=1$ if the home state recognizes the secessionists as independent, $Y=0$ otherwise.

Player $p$'s payoffs in period $t$ are $U_p^t= -\alpha X+\lambda Y -R_p^t$, while the payoffs for player $c$ are $U_c^t= \beta X-\nu Y -R_c^t$, with both payoffs denoted in currency units. Taking $\alpha, \ \beta, \lambda,$ and $\nu$ to be positive, these payoffs represent the idea that the patron opposes reunification while player $c$ prefers it, and that the patron prefers recognized independence while player $c$ is averse to the creation of new states.

@@

First, note that the restrictions in Definition 1 are sufficient but not necessary. For example, if the status quo initially has a much higher long term payoff than the next best alternative for the secessionists, Restriction (\ref{res:6}) need not be met to maintain the status quo in the short run. The inequality \emph{will} bind for some set of periods $t \geq 1$ because the secessionist payoffs from the status quo decrease over time. In cases where Restriction (\ref{res:6}) is not met, we can have unrecognized statehood for some time, but it is not a long-run equilibrium outcome.

@@

There are at least two takeaways from the multiplicity of equilibrium outcomes. First, it indicates that there may be an important role for external actors to play in coordinating expectations about which equilibrium will be played, and in the absence of such coordination, equilibrium switching from the status quo equilibrium to one of the other outcomes is possible. Second, most of the types of outcomes that we observe in the post-WWII era are consistent with the set of parameters outlined in Proposition 1 that support the status quo outcome.

>>>>

All the state variables except for the secessionists' status quo payoffs remain unchanged from period to period unless players $p$ or $c$ make an investment. The status quo payoffs for the secessionists are special in that the transition of this state variable from one period to the next involves an automatic reduction by $\mu$. The steady reduction by $\mu$ represents the costs of non-recognition discussed in the introduction.

Only two outcomes of the stage game do not lead to absorbing states, and the payoffs for these are bolded. If both $s$ and $g$ play Status Quo, then the status quo persists. Likewise, if both states simultaneously play Cede, we assume that both renege immediately and that the status quo is preserved for that period. In this case neither player has demonstrated a willingness to give up more than the other. Therefore, payoffs for both players ceding simultaneously are identical to the status quo payoffs.

@@

The patron opposes reunification while player $c$ prefers it, and the patron prefers recognized independence while player $c$ is averse to the creation of new states.

@@

First, note that the restrictions in Definition 1 are sufficient but not necessary. For example, if the status quo initially has a much higher long term payoff than the next best alternative for the secessionists, Restriction (\ref{res:6}) need not be met to maintain the status quo in the short run. The inequality \emph{will} bind for some set of periods $t \geq 1$ because the secessionist payoffs from the status quo decrease over time.

@@

There are at least two takeaways from the multiplicity of equilibrium outcomes. First, it indicates that there may be an important role for external actors to play in coordinating expectations about which equilibrium will be played, and in the absence of such coordination, equilibrium switching from the status quo equilibrium to one of the other outcomes is possible. Second, most of the types of outcomes that we observe in the post-WWII era are consistent with the set of restrictions outlined in Proposition 1 that support the status quo outcome.
